Do Reddit /r/depression Authors who Pen Suicidal Ideation Leave Reddit at Higher Rates?

### 2016-10-24 Paper_Rough_Draft.Rmd
Finalize EDA
Reran classifier on authors data summary. Added authors without SI.

```{r setup, include=FALSE}
require(ggplot2); require(dplyr); require(reshape2)
options(width = 90)
options(digits = 4)
```

@@

@@

```{r , echo=FALSE, message=FALSE, warning=FALSE}
load(file="Data/SI_Author_Sample/June_Authors_Data_Classified.RData")
author.sum =
      user.data %>%
      group_by(author, type) %>%
      summarise(oldest = min(date),
                prop.dep.post = mean(r.depression, na.rm=T),
                n.post = n()) 
author.sum2 = 
      user.data %>% 
      group_by(author) %>%
      summarise(oldest = min(date, na.rm=T),
                newest = max(date, na.rm=T),
                prop.dep.post = mean(r.depression, na.rm=T),
                n_si = sum(class, na.rm=T),
                n.post = n())
user.data = 
      transmute(author.sum2, author, 
                rank_oldest = rank(oldest),
                rank_newest = rank(newest),
                rank_n = rank(n.post,ties.method = "random"),
                rank_prop = rank(prop.dep.post,ties.method = "random")) %>%
      merge(user.data, by = "author", all.y=T)
user.data$point.label = 
      ifelse(user.data$class, "SI",
      ifelse(user.data$r.depression, "/r/depression","other")) %>%
      ordered(labels = c("other", "/r/depression", "SI"))

get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
july1 = get.date("2016-07-01 00:00:00")
june1 = get.date("2016-06-01 00:00:00")
jan1 = get.date("2016-01-01 00:00:00")
ggplot() +
geom_point(data = subset(user.data, date > jan1),
           aes(y=rank_newest,x=date, 
               color=point.label, alpha=point.label, 
               size=point.label)) + 
ggtitle("Distribution of Post Dates across Authors\nbetween Jan. and Oct.") +
ylab("Author Rank by Newest Post") + xlab("Date") +
geom_vline(aes(xintercept = as.numeric(july1)), alpha=0.3) + 
geom_vline(aes(xintercept = as.numeric(june1)), alpha=0.3) + 
scale_colour_manual(values = c("grey","darkblue", "red")) + 
scale_size_manual(values = c(0.1,0.1,0.3)) + 
scale_alpha_manual(values = c(0.1,0.1,1)) + 
theme_bw()
```

>>>>

```{r setup, include=FALSE}
require(ggplot2); require(dplyr); require(reshape2)
options(width = 90)
options(digits = 4)
load("June_Authors_Combined.RData")
```

@@

Another potential es

@@

```{r , echo=FALSE, message=FALSE, warning=FALSE}
user.data = 
      author.summary %>%
      group_by(author) %>%
      filter(newest == max(newest)) %>%
      ungroup %>%
      group_by(si.author)%>%
      transmute(author, rank_newest = rank(newest)) %>%
      ungroup %>%
      select(-si.author) %>%
      merge(user.data, by = "author", all.y=T)
user.data$point.label = 
      ifelse(user.data$class, "SI",
      ifelse(user.data$r.depression, "/r/depression","other")) %>%
      ordered(labels = c("other", "/r/depression", "SI"))
user.data$si.group = 
      ifelse(user.data$si.author, "SI-Positive in June /r/depression",
             "SI-Negative in June /r/depression")
### Make plot
ggplot(data = subset(user.data, date > jan1)) +
geom_point(aes(y=rank_newest,x=date, 
               color=point.label, alpha=point.label, 
               size=point.label)) + 
ggtitle("Distribution of Post Dates across Authors\nbetween Jan. and Oct.") +
ylab("Author Rank by Newest Post") + xlab("Date") +
geom_vline(aes(xintercept = as.numeric(july1)), alpha=0.3) + 
geom_vline(aes(xintercept = as.numeric(june1)), alpha=0.3) + 
scale_colour_manual(values = c("grey","darkblue", "red")) + 
scale_size_manual(values = c(0.1,0.1,0.3)) + 
scale_alpha_manual(values = c(0.1,0.1,1)) + 
theme_bw() + facet_wrap("si.group")
```
